---
title: "DDP Shiny App Presentation"
author: "Kurtis Pivert"
date: "5/20/2017"
output: ioslides_presentation
---

```{r setup, include=FALSE, message=FALSE, warning=FALSE}
        ## Load Required Packages 
        require(knitr)
        require(plotly)
        require(tidyverse)
        require(extrafont)
        loadfonts(quiet = TRUE)
        data("cars")
```

## DDP: Kurtis Pivert Shiny App Project  

This presentation outlines the motivation for, and function of, the rudimentary 
Shiny App developed for the Developing Data Products final project.  

The Shiny App I created provides:

- Brief Motivation and Outline for Using Simple Linear Regression
- Basic App for Creating a Simple Linear Model Using Random Variables
- Illustration of How Data Can Affect Regression Line 
- Basic Illustration of How to Use Linear Models for Prediction 

## Why Should You Use the App? 

- The interactivity provided by the Shiny App interface is pretty cool
- The App illustrates the utility of using simple linear models for simple data sets


## Plot of Simple Linear Model 
```{r Plot 1, echo=TRUE, message=FALSE, warning=FALSE}
        
ggplotly(ggplot(cars, aes(x = speed, y = dist))+geom_point(color = "blue", alpha = 0.5)+
geom_smooth(method = "lm")+theme_bw(base_family = "Roboto")+xlab(label = "Speed in MPH")+
ylab(label = "Stopping Distance in Feet"))
```

## Thanks for Your Review

I welcome your comments and suggestions for improvement. Please email me at
[kurtis.pivert@gmail.com](mailto:kurtis.pivert@gmail.com).
